Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-11-22 ms/ms.Rmd
add calibration plots

>>>>

The best models at both sites strongly underpredicted the deepest peats (Fig. \@ref(fig:calPlots)).

```{r calPlots, echo = FALSE, fig.cap = "Calibration plots for the best-performing models at Skrimfjella (a) and Ørskogfjellet (b), with predictions from spatial cross-validation. Blue smoother lines are local polynomial regressions. Marginal distributions are shaded by quartile."}
knitr::include_graphics("figures/calibration_plots.pdf")
```

### 2024-11-22 ms/ms.tex
add calibration plots

>>>>

The best models at both sites strongly underpredicted the deepest peats (Fig. \ref{fig:calPlots}).

\begin{figure}
\centering
\includegraphics{figures/calibration_plots.pdf}
\caption{\label{fig:calPlots}Calibration plots for the best-performing models at Skrimfjella (a) and Ørskogfjellet (b), with predictions from spatial cross-validation. Blue smoother lines are local polynomial regressions. Marginal distributions are shaded by quartile.}
\end{figure}
